Verified Time Balancing of Security Protocols \\ \large A Case Study

### 2018-12-20 Src/paper.tex
Updated simplified model of ZRTP, still need to write up DH Part 1 and 2 though!

@@

@@

          type DH2k, p=2048 Bit Prime as per RFC 3526.

@@

  \subsubsection{The Hello and HelloAck Messages}

@@

  verifying timing observability.

>>>>

  \newpage

@@

  This section details a simplified model of the ZRTP protocol with the
  purpose of identifying relevant computation for timing observability.

@@

          type DH3k, p=3072 Bit Prime as per RFC 3526 section 4.

@@

  \subsection{The Hello and HelloAck Messages}

@@

  timing observability. \\
  while $h3$ can be precalculated, it is important for the responder
  to send this to the initiator as this allows the responder to validate
  against the initiators DH Part 2 message.
    \item Let $h0$ represent a 256 bit random nonce.
    \item Let $h1$ represent SHA-256 of $h0$
    \item Let $h2$ represent SHA-256 of $h1$
    \item Let $h3$ represent SHA-256 of $h2$
  \subsubsection{Alice sends Hello}
  $alice_0(h3_{a0})$
  \subsubsection{Bob sends Hello}
  $bob_0(h3_{b0})$
  Given the assumptions above, the commit message contains the following
  components that are required to be computed by the initiator.
    \item Let $hvi$ represent the initiators hash value under DH3k key
      agreement type, such that:
        \item Let $svi$ represent a random 3072 bit number under the DH3k key
              agreement type.
        \item Let $p = 2^{3072} - 2^3008 - 1 + 2^64(2^2942\pi + 1690314)$ represent
              the prime number under the DH3k key agreement type.
        \item Let $g = 2$ represent the generator under the DH3k key agreement
              type.
        \item Let $pvi = mod(g^svi, p)$ represent the public value of the
              initiator.
        \item Let $dh2i$ represent the precalculation of the DH Part 2 message
              by the initator in order to compute part of the $hvi$.
        \item Let $h3_{a0}$ represent Alice's Hello message that Bob has
              received.
        \item Then $hvi = ha(dh2i||h3_{a0})$ 
  \subsubsection{Bob precalculates DH Part 2}
  $bob_1=(h3_{b0},pvi)$
  $bob_2(h2_{b1},hvi)$
